---
title: "Getting started with frite"
author: "Christopher Peralta"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
#Introduction

**frite** is a package that enables us to easily write and modify functions. It can be used to inject, assign, or remove code in a function.  There are also functions that enable you to use this package more easily. You can use the diagnostic functions to test any function that you can think of. 


#The functions

Diagnostic
  * `tictocify` *returns a nearly identical timed version of its input*
  * `is.output.same` *performs call on multiple functions and sees if they match*
  
Modification
  * `line_assign` *inserts `assign()` into a function*
  * `line_insert` *inserts code into a function*
  * `line_remove` *removes code from a function*
  * `copy_args` *copies the arguments of one function to another*
  
Helping
  * `list_body` *converts function body to a list*
  * `plot_body` *plots `list_body()` so you can inspect the body*




## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```



